### 2015-02-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2102: Added Figure for Burn Building
DelCo 2012: Spray Density CSV files, updated matlab scripts, updated report (tables)

@@

@@

Each 
12 Experiments:
4 SS from room
2 Fog from room
2 SS from Hall
2 Fog from Hall
1 SB from Hall
1 SB from Room

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingDimensions}
	\caption{Delaware County, PA Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Temperature Comparison}
	\begin{tabular}{ll}
		\hline\noalign{\smallskip}
		Temperature				 & Response		\\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
		100 deg C (212 deg F)    & Water boils and produces steam    \\
		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Temperature_Comparison}
\end{sidewaystable}

\begin{sidewaystable}[!ht]
	\centering
	\caption{Heat Flux Comparison}
	\begin{tabular}{ll}
		\hline\noalign{\smallskip}
		Heat Flux	  				   & Response		\\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1 kW/m\textsuperscript{2}      & Sunny day      \\
		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Heat_Flux_Comparison}
\end{sidewaystable}

@@

12 Experiments:
4 SS from room
2 Fog from room
2 SS from Hall
2 Fog from Hall
1 SB from Hall
1 SB from Room
